\documentclass[11pt,a4paper]{moderncv}
% moderncv themes
\moderncvtheme[blue]{classic}
% character encoding
\usepackage[utf8]{inputenc}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{ngerman}

\setlength{\hintscolumnwidth}{3.7cm}
\recomputelengths
% personal data
\firstname{Maximilian}
\familyname{Kürschner}
\title{Curriculum Vitae}
\address{Rheinhessenring 10}{55597 Wöllstein}
\email{mail@maximilian-kuerschner.de}

\begin{document}
\maketitle

\vspace*{-5mm}

\section{Education}
\cventry{Sep. 2021 - present}{Master of Science}{University of Applied Sciences}{Mannheim}{Informatics - Software Engineering}{Current Grade: 1.1}
\cventry{Jul. 2018 - Sep. 2021}{Bachelor of Science}{Cooperate University Baden-Württemberg}{Mannheim}{Informationtechnologies}{Grade: 1.6}
\cventry{2009 - 2018}{Abitur}{Lina Hilger Gymnasium}{Bad Kreuznach}{}{Grade: 2.3}

\section{Professional Career}
\cventry{Jul. 2022 - present}{App Developer (Freelance)}{future.self gGmbH}{Remote}{}{}
\cventry{Oct. 2021 - Dec. 2021}{Associate Project Engineer}{ABB Automation GmbH}{Mannheim}{}{}
\cventry{Jul. 2018 - Sep. 2021}{Coorperate Student Informationtechnologies}{ABB Automation GmbH}{Mannheim}{}{}

\section{Software Skills}
\cvitem{Programming Languages}{Python, JavaScript, C\#, Dart, Rust, C, Java}
\cvitem{Tools}{Microsoft Office, Unity, Git, Docker}{}{}
\cvitem{Other}{Machine Learning, DevOps, CI/CD}{}{}

\section{Languages}{}
\cvlanguage{German}{Native Tongue}{}
\cvlanguage{English}{Proficent}{}

\section{Projects}
\cventry{May 2021 - present}{\href{https://www.programonaut.com}{Programonaut.com}}{Blog about software development}{Personal Project}{}{}
\cventry{Jan 2022 - Feb 2022}{\href{https://slide-for-four.de/}{Slide For Four}}{Slide Puzzle Game}{Flutter Puzzle Hack - Hackathon}{}{Winner - Honorable Mention}
\cventry{Mar 2022 - May 2022}{\href{https://easy-portfolio.com/}{Easy Portfolio}}{Generate Portfolio Websites from GitHub Profiles}{Personal Project}{}{}
\cventry{Jan 2020 - Dec 2020}{\href{https://play.google.com/store/apps/details?id=com.Deved.Bralls}{Bralls}}{Arcade Mobile Game}{Personal Project}{}{}

\cventry{Sep 2021 - Jun 2022}{\href{https://sugar-network.org/projects}{ME310 Sugar Project for Design and Innovation}}{DAMU - Medical Teleconsultation for Elderly}{University Project in collaboration with Paris d.school}{}{}
\cventry{Mar 2022 - Jul 2022}{\href{https://github.com/programonaut/ball-schubser}{Autonomous Mobile Robots}}{Robot that detects a ball and brings it to a goal}{University Project}{}{}

\end{document}
